Relating two Abstractions for Formal Array Languages

### 2014-04-11 paper.tex
updated the abstract
What do you think?

\begin{abstract}
This is the text of the abstract.
\end{abstract}

>>>>

\begin{abstract}
The aim of this paper is to rectify some of the fragmentation
within the high-performance array programming community. We look at two
formalisms for functional, high-performance array computations:
Mathematics of Arrays and Pull arrays, two seemingly different formalisms
that share many principles and properties.   This paper is meant to
identify the striking similarities between the two  and to act as a guide  to enable research communications.

\end{abstract}
